---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  cache = TRUE
)

library(ffsimulator)
library(dplyr)
library(ggplot2)

this_season <- 2022
espn_league <- 31003357
num_seasons <- 1000
num_weeks   <- 14
rand_seed   <- 1914
```

# No Allys Here: 2022 Fantasy Football Season

<!-- badges: start -->

<!-- badges: end -->

This repository holds full season and weekly simulations for the No Allys Here 2022 Fantasy Football season.

## Full Season Simulation

```{r}
conn <- espn_connect(season = this_season, league_id = espn_league)

espn_sim <- ff_simulate(
  conn, 
  n_seasons = num_seasons,
  n_weeks   = num_weeks,
  seed      = rand_seed
)
```

```{r}
#> Wins
wins_tbl <- espn_sim$summary_season %>% 
  as_tibble() %>% 
  group_by(franchise_name) %>% 
  summarize(median_wins = median(h2h_wins, na.rm = TRUE)) %>% 
  ungroup()

wins <- max(wins_tbl$median_wins)

result_wins <- wins_tbl %>% 
  filter(median_wins == max(median_wins)) %>%
  arrange(franchise_name) %>% 
  pull(franchise_name) %>% 
  paste(collapse = ", ")


#> Ranking
rank_tbl <- espn_sim$summary_season %>% 
  as_tibble() %>%
  group_by(season) %>% 
  mutate(season_rank = rank(-h2h_wins, ties.method = "min")) %>% 
  ungroup() %>%
  group_by(franchise_name) %>% 
  count(season_rank) %>% 
  filter(season_rank == 1) %>% 
  ungroup() %>% 
  filter(n == max(n))

rank <- max(rank_tbl$n)

result_rank <- rank_tbl %>% 
  arrange(franchise_name) %>% 
  pull(franchise_name) %>% 
  paste(collapse = ", ")


#> Points
points_tbl <- espn_sim$summary_week %>% 
  as_tibble() %>% 
  group_by(franchise_name) %>% 
  summarize(median_points = median(team_score, na.rm = TRUE)) %>% 
  ungroup()

points <- ceiling(max(points_tbl$median_points))

result_points <- points_tbl %>% 
  filter(median_points == max(median_points)) %>% 
  arrange(franchise_name) %>% 
  pull(franchise_name) %>% 
  paste(collapse = ", ")
```

The overall results of simulating the `r this_season` season `r num_seasons` times are shown below.

|         Metric          |       Team        |   Value    |
|:-----------------------:|:-----------------:|:----------:|
|  Wins (season median)   |  `r result_wins`  |  `r wins`  |
| Rank (most #1 finishes) |  `r result_rank`  |  `r rank`  |
| Points (weekly median)  | `r result_points` | `r points` |

### Wins

Distribution of total season wins for each team from `r num_seasons` simulations of the `r this_season` season.

```{r}
autoplot(espn_sim, type = "wins") + scale_fill_viridis_d()
```

### Final Ranking

Distribution of final ranking for each team from `r num_seasons` simulations of the `r this_season` season.

```{r}
autoplot(espn_sim, type = "rank") + scale_fill_viridis_d()
```

### Total Points

Distribution of average number of weekly points for each team from `r num_seasons` simulations of `r this_season` season.

```{r}
autoplot(espn_sim, type = "points") + scale_fill_viridis_d()
```

## Weekly Simulations

| Week | Link                           |
|:----:|:------------------------------:|
|  1   | [Simulation Result](/Week 1/)  |
|  2   | [Simulation Result](/Week 2/)  |
|  3   | [Simulation Result](/Week 3/)  |
|  4   | [Simulation Result](/Week 4/)  |
|  5   | [Simulation Result](/Week 5/)  |
|  6   | [Simulation Result](/Week 6/)  |
|  7   | [Simulation Result](/Week 7/)  |
|  8   | [Simulation Result](/Week 8/)  |
|  9   | [Simulation Result](/Week 9/)  |
|  10  | [Simulation Result](/Week 10/) |
|  11  | [Simulation Result](/Week 11/) |
