---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  fig.align = "c"
)

library(ffsimulator)
library(dplyr)
library(ggplot2)
library(kableExtra)

this_season <- 2022
this_week   <- 1
espn_league <- 31003357
num_iter    <- 100
rand_seed   <- 1914
```

# 2022 Fantasy Football Season: Week `r this_week`

<!-- badges: start -->

<!-- badges: end -->

```{r}
conn <- espn_connect(season = this_season, league_id = espn_league)

espn_wk1_sim <- ff_simulate_week(conn, n = num_iter, seed = rand_seed)
```

```{r}
#> Points
points_tbl <- espn_wk1_sim$summary_week %>% 
  as_tibble() %>% 
  group_by(franchise_name) %>% 
  summarize(
    median_points_for = median(team_score, na.rm = TRUE),
    median_points_against = median(opponent_score, na.rm = TRUE)
  ) %>% 
  ungroup()

points_for <- round(max(points_tbl$median_points_for))
points_against <- round(min(points_tbl$median_points_against))

result_points_for <- points_tbl %>% 
  filter(median_points_for == max(median_points_for)) %>% 
  arrange(franchise_name) %>% 
  pull(franchise_name) %>% 
  paste(collapse = ", ")

result_points_against <- points_tbl %>% 
  filter(median_points_against == min(median_points_against)) %>% 
  arrange(franchise_name) %>% 
  pull(franchise_name) %>% 
  paste(collapse = ", ")
```

The overall results of simulating Week `r this_week` season `r num_iter` times are shown below.

| Metric                | Team                      | Value              |
|:---------------------:|:-------------------------:|:------------------:|
| Highest Points For    | `r result_points_for`     | `r points_for`     |
| Lowest Points Against | `r result_points_against` | `r points_against` |

## Predicted Results

The predicted win/loss and points for Week `r this_week` after `r num_iter` simulations.

```{r}
espn_wk1_sim$summary_week %>% 
  as_tibble() %>% 
  group_by(franchise_name, opponent_name) %>% 
  summarize(
    med_team_score = round(median(team_score, na.rm = TRUE), 0),
    med_opp_score  = round(median(opponent_score, na.rm = TRUE), 0)
  ) %>% 
  ungroup() %>% 
  filter(med_team_score >= med_opp_score) %>% 
  rename(
    `Team 1` = franchise_name,
    `Team 2` = opponent_name,
    `Team 1 Score` = med_team_score,
    `Team 2 Score` = med_opp_score
  ) %>% 
  kable(align = "c") %>% 
  kable_styling("hover", full_width = FALSE, position = "center")
```

## Predicted Points

Distribution of predicted number of points for Week `r this_week` after `r num_iter` simulations.

```{r}
autoplot(espn_wk1_sim, type = "points") + scale_fill_viridis_d()
```
